Supplementary Information

### 2020-09-02 doc/manuscript/MEE_manuscript_SI.Rmd
add info to table S5

```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
ss_table <- read.csv("tables_figures/qualitative_results_comparison.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(ss_table, format = "latex", booktabs = TRUE,   escape = F, linesep = c('\\addlinespace'))%>%
  add_header_above(c(" "," ", "Precipitation response" = 2, "Temperature response" = 2)) %>%
  column_spec(3, width = "4cm") %>%
  column_spec(4, width = "4cm") %>%
  column_spec(5, width = "4cm") %>%
  column_spec(6, width = "4cm") %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), protect_latex = T)

# refs in this table need to go in the nocite field below
```
---
nocite: | 
  @alfaro-sanchez_growth_2017; @vlam_temperature_2014; @helcoski_growing_2019; @maxwell_declining_2016; @aus_de_ar_tree_2018; @bumann_assessing_2019; @tumajer_increasing_2017; @sniderhan_growth_2016
---
Results from this study are the climate-only model. 
For previous studies, we summarize responses only within the months considered here. 
Beyond the methodological differences, original studies vary from this one and from one another in factors including
exact set of cores analyzed,
climate data sources,
time frame of analysis,
approaches to identifying candidate climate variables and windows (including whether this is done on a site or species level), 
methods for detrending and standardizing to build chronologies,
and whether the effects of temperature and precipitation are considered separately (original studies) or additively (this study).
An analysis standardizing all of these factors for four species is present in Appendix **S2** and Fig. **S1**.

>>>>

```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
ss_table <- read.csv("tables_figures/qualitative_results_comparison.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(ss_table, format = "latex", booktabs = TRUE, longtable = TRUE,  escape = F, linesep = c('\\addlinespace'))%>%
  add_header_above(c(" "," ", "Precipitation response" = 2, "Temperature response" = 2)) %>%
  column_spec(3, width = "2.5cm") %>%
  column_spec(4, width = "2.5cm") %>%
  column_spec(5, width = "2.5cm") %>%
  column_spec(6, width = "2.5cm") %>%
  column_spec(7, width = "2cm") %>%
  kable_styling(latex_options = c( "hold_position", "repeat header"), protect_latex = T, font_size = 9)

# refs in this table need to go in the nocite field below
```
---
nocite: | 
  @alfaro-sanchez_growth_2017; @vlam_temperature_2014; @helcoski_growing_2019; @maxwell_declining_2016; @aus_de_ar_tree_2018; @bumann_assessing_2019; @tumajer_increasing_2017; @sniderhan_growth_2016
---
Results from this study are the climate-only model. 
Where previous studies examined numerous climate variables or time windows [e.g., @helcoski_growing_2019], we focus on those most relevant to our findings. 
Beyond the methodological differences, original studies vary from this one and from one another in factors including
exact set of cores analyzed,
climate data sources,
time frame of analysis,
approaches to identifying candidate climate variables and windows (including whether this is done on a site or species level), 
methods for detrending and standardizing to build chronologies,
and whether the effects of temperature and precipitation are considered separately (original studies) or additively (this study).
An analysis standardizing all of these factors for four species is present in Appendix **S2** and Fig. **S1**.
